Benchmarking Python Deep Learning Frameworks\\ on Language Modeling

### 2016-12-13 paper/main.tex
add dynet numbers

We profile which methods take the most amount of time, and look into a variety of metrics.
\begin{itemize}
\item \verb!achieved_occupancy! - fraction of GPU warps used v.s. total number of warps
\item \verb!sm_efficiency! - how much of the runtime is spent performing actual computation
\item \verb!warp_execution_efficiency! - how efficient is execution within a warp; number of registers per thread is a limiting factor.
\item \verb!warp_nonpred_execution_efficiency! - how efficient is execution within a warp on non-predicated (i.e. non-branching) instructions.
\item \verb!dram_read_throughput! - read throughput
\item \verb!dram_write_throughput! - write throughput
\end{itemize}
\section{Discussion}
When looking to use neural network benchmarks, researchers might want to consider various aspects.
\subsection{Programmer Experience}
When adopting new software frameworks, it is important to consider the potential learning curve, as well as higher-level advantages of each framework.
\subsubsection{DyNet}

>>>>

We profile which methods take the most amount of time, and look into a variety of metrics.
\begin{itemize}
\item \verb!achieved_occupancy! - number of GPU warps used vs. total number of warps available
\item \verb!sm_efficiency! - how much of the runtime is spent performing actual computation
\item \verb!warp_execution_efficiency! - how efficient is execution within a warp; number of registers per thread is likely a limiting factor for all implementations.
\item \verb!warp_nonpred_execution_efficiency! - how efficient is execution within a warp on non-predicated (i.e. non-branching) instructions.
\item \verb!dram_read_throughput! - read throughput from RAM to GPU
\item \verb!dram_write_throughput! - write throughput from GPU to RAM
\end{itemize}
\section{Discussion}
When looking to use neural network benchmarks, researchers might want to consider various aspects.
\subsection{Programmer Experience}
When adopting new software frameworks, it is important to consider the potential learning curve, as well as higher-level advantages of each framework.
\subsubsection{DyNet}
